\section{Requirements}

\paragraph{Classroom}

You must complete all the readings for the course and attend class
prepared to discuss them.

\paragraph{Response Posts to Blackboard}

6 times in the semester, you will post a short \emph{response} to one or
more of the readings for that day on Blackboard. These must be posted by
5pm the day \emph{before} class meets so that your peers have time to
read them. You must also write 6 \emph{responses} to your peer's posts.
Both posts and responses will be included as part of your participation
grade.

\paragraph{Papers}

You will write one 5 to 7 page paper for this class, based on the
readings; no outside research is expected.

\paragraph{Archival Project}

Mid-semester, we will take a trip to the university archives to look at
some archival documents. You will write up a description of another
document from elsewhere in the archives. This can take the form of a
straightforward narration, or you can adapt the information

\paragraph{Final Project}

Final project assignments will be distributed in October, but you should
start thinking early about which one you will want. It will consist of
either 1) an 8-10 page paper in which you extend one of the weeks of the
course with additional readings; or 2) a digital project in which you
analyze a dataset created before the year 1994 using modern tools. In
either case, you must discuss the project in advance with me.

\section{Academic Integrity}

You are expected to have read, and follow at all times, the University's
\href{http://www.northeastern.edu/osccr/academicintegrity/index.html}{Academic
Integrity Policy}.
