\section{Schedule and Readings}

\subsection{Required for purchase: these will be placed in the
University bookstore, but you will probably be better off ordering used
or new copies online.}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Tracy Kidder, \emph{The Soul of a New Machine}
\item
  Sarah Igo, \emph{The Averaged American}
\item
  Nicholas Lehman, \emph{The Big Test}
\item
  Frederick Taylor, \emph{The Principles of Scientific Management}
\item
  Tim Berners-Lee, \emph{Weaving the Web}
\end{itemize}

All other readings will be made available through Blackboard.

In addition to the readings listed below, some short primary sources may
be added to Blackboard as the course develops to accompany a week's
readings.

\subsection{September 5: Introductions}

\subsection{September 9 and 12: Early Modern Information Overload}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite{blair_reading_2003}
\item
  \cite{muller-wille_natural_2012}
\end{itemize}

\subsection{September 16 and 19: Ordering the World}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite{borges_analytical_1999}
\item
  \cite[Introduction and Chapter 3]{foucault_order_1994}
\end{itemize}

Look carefully at the collection of 19th century statistical graphics
online; possible additional selections from Edward Tufte.

\subsection{September 23 and 26: Counting and Business in the 19th
Century}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite{edwards_early_1960}\\
\item
  \cite{garvey_facts_2013}
\item
  Fogel and Engerman, on the efficiency of slavery
\item
  GW Hammond, Instructions to his Overseer
\end{itemize}

\subsection{September 30: Industrial Information}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite[selections]{beniger_control_1986}
\end{itemize}

\subsubsection{October 3: The Census}

\textbf{First Paper Assignments handed out.}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite{kinnahan_charting_2008}
\item
  \cite[Chapters 3 to 5]{anderson_american_1988}
\end{itemize}

\subsection{October 7 and 10: Sciences of Management}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite{taylor_principles_2006}
\item
  \cite[Chapters 5 and 6]{meyer_five_1981}
\end{itemize}

\subsection{October 17: Technocracy}

(No class October 14/Columbus Day)

\textbf{Short Papers Due Wed. October 16 at noon in the History
Department or as an e-mailed PDF}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Parrish, Wayne. ``What is Technocracy?'' New Outlook 161 (Nov 1932):
  13-18.
\item
  Scott, Howard. ``Technocracy Speaks.'' Living Age 343 (Dec 1932):
  297-303.
\item
  MacLeish, Archibald. ``Machines and the Future.'' The Nation 136 (8
  Feb 1933): 140-142.
\item
  Jordan, Virgil. ``Technocracy - Tempest on a Slide Rule.'' Scribner's
  Magazine 93 (Feb 1933): 65-69.
\end{itemize}

\subsection{October 21 and 24: A culture of data}

\textbf{Data exploration Assignments handed out: Due October 31}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite[Chapters 5 and 6]{igo_averaged_2007}
\item
  \cite[pp. 1-122]{lemann_big_1999}
\item
  \cite[pp 193-229]{ohmer_george_2006}
\end{itemize}

\subsection{October 28 and 31: The Computer enters the scene.}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite{bush_as_1945}
\item
  \cite{bush_memex_1991}
\item
  \cite{lubar_not_1992}
\item
  Cosmpolitan, ``The Computer Girls,'' 1967
\item
  \cite[Chapter TBD]{ensmenger_computer_2010}
\item
  \cite{light_when_1999}
\end{itemize}

Film selections: ``The Desk Set''

\subsection{November 4 and 7: Computers in the Mainstream}

\textbf{Final Project Discussion}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite[Selections]{miller_assault_1971}
\item
  \cite{kidder_soul_1981}
\end{itemize}

\subsection{November 14: Personal Computers and the Web}

(No class November 11/Veterans' Day)

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Stewart Brand (ed.) \emph{The Whole Earth Catalog} (selections)
\item
  Ted M. Lau, ``Total Kitchen Information System'', 1977
\item
  \cite[Introduction; Chapters 1, 2, and 3]{berners-lee_weaving_1999}
\end{itemize}

\subsection{November 18 and 21: The Data Deluge and the Age of Google}

\begin{itemize}
\item
  \cite["After the Deluge"]{gleick_information_2011}
\item
  The End of Theory, Wired Magazine (Read the Introduction and pick two
  fields you are interested in to discuss in class)
\item
  \cite[Chapter 2]{vaidhyanathan_googlization_2011}
\item
  \href{http://norvig.com/chomsky.html}{Noam Chomsky on Machine
  Learning, and Peter Norvig on Noam Chomsky}
\end{itemize}

\subsection{November 25: December Surveillance and the state}

\textbf{Final Project brief description submission deadline}

(No class November 28/Thanksgiving)

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \cite[Networked Authoritarianism]{mackinnon_consent_2012}
\item
  NSA Prism documents
\item
  \href{http://www.youtube.com/watch?v=5yB3n9fu-rM}{Watch Edward
  Snowden's interview with Glenn Greenwald}
\item
  \href{http://www.thisamericanlife.org/radio-archives/episode/493/picture-show?act=1}{Listen
  to ``Photo Op,'' \emph{This American Life} Episode 493}
\item
  Cory Doctorow,
  \href{http://boingboing.net/2012/01/10/lockdown.html}{``Lockdown: The
  Coming War on General-Purpose Computing''}
\end{itemize}

\subsection{December 4: TBD/Catchup.}

\textbf{Final Projects Due December 5}
